Benchmarking figures

### 2016-05-04 results/figures.Rmd
fixes formating issues caused by SRA fastq names and such

######### Hiseq roc functions ##########
hiseq.roc<-function(sum.df,possible_tp,possible_vars,direction){ # A function to run the roc calculations and adjustments
  roc.ls<-dlply(sum.df,~Id,sum_roc,direction)

@@

hiseq.roc.table<-function(sum.df,cut.off,possible_tp,possible_vars,direction){
  roc.ls<-dlply(sum.df,~Id,sum_roc,direction)
  roc.df<-roc_df.one(roc.ls,cut.off)
  roc.df.adj<-ddply(roc.df,~samp,adjust.coords,sum.df,possible_tp,possible_vars)
mutate(roc.df.adj, gc = as.numeric(sub(pat,"\\1",samp)),
       exp.freq = sub(pat,"\\2",samp)
)-> roc.df.adj

@@

lofreq.df<-mutate(lofreq.df,mutation=paste0(CHROM,"_",REF,POS,ALT))
lofreq.df<-mutate(lofreq.df,category=mutation %in% true_snv$mutant,Id=ID)
lofreq.df$category[lofreq.df$mutation %in% wt_mut]<-"wt"
lofreq.df$category[lofreq.df$mutation %in% mfe.df$mutation]<-"mfe"

lofreq.df$p.val<-as.numeric(lofreq.df$QUAL) # to make the roc based on the quality scores given by lofreq
lofreq.roc<-hiseq.roc(lofreq.df,possible_tp,possible_vars,"<")

@@

#knitr::kable(subset(lofreq.table,gc==5,select=c(exp.freq,TP,FP)))
lofreq.table<-head(subset(lofreq.table,gc==5,select=-c(gc,Id)),n=-1) # don't need the 0.1% sample
rename(lofreq.table,c("exp.freq"="Frequency","TP"="True\nPositives","FP"="False\nPositives"))->lofreq.table
lofreq.table$Frequency<-c("5.0%","2.0%","1.0%","0.5%","0.2%")
lofreq.table$Sensitivity<-round(lofreq.table$Sensitivity,digits=dd)
lofreq.table$Specificity<-round(lofreq.table$Specificity,digits=dd)
lofreq.table<-subset(lofreq.table,select=c("Frequency","Sensitivity","True\nPositives","Specificity","False\nPositives"))
tt2<-ttheme_minimal(colhead=list(fg_params=list(fontface=1,cex=0.65,fontfamily="serif")),core=list(fg_params=list(cex=0.65,fontfamily="serif")))

@@

dup.df<-mutate(dup.df,category=mutation %in% true_snv$mutant) # add Column for True and false variants
dup.df$category[dup.df$mutation %in% wt_mut]<-"wt"

@@

```{r,results="asis",cache=F}
tabulate(5,c(0.05,0.01,0.005))
#

@@

x<-join(x,y)
x<-subset(x,!(Id%in% c(1240,1241)))
x<-x[order(x$`log10(gc_ul)`,decreasing = T),]
write.csv(x,"../results/tables/table_2.cali_vic.csv")
ggplot(data,aes(pos,freq.var))+geom_point()+facet_wrap(~chr)

ggplot(data.cut,aes(pos,freq.var))+geom_point()+facet_wrap(~chr)

ggplot(data,aes(freq.var))+geom_histogram()+scale_x_log10()

ggplot(data.cut,aes(freq.var))+geom_histogram()+scale_x_log10()+scale_y_log10()

@@

>>>>

######### Hiseq roc functions ##########
hiseq.roc<-function(sum.df,possible_tp,possible_vars,direction){ # A function to run the roc calculations and adjustments
  pat<-"([0-9]+)_([0-9]+)"
  roc.ls<-dlply(sum.df,~Id,sum_roc,direction)

@@

hiseq.roc.table<-function(sum.df,cut.off,possible_tp,possible_vars,direction){
  pat<-"([0-9]+)_([0-9]+)"
  roc.ls<-dlply(sum.df,~Id,sum_roc,direction)
  roc.df<-roc_df.one(roc.ls,cut.off)
  roc.df.adj<-ddply(roc.df,~samp,adjust.coords,sum.df,possible_tp,possible_vars)
mutate(roc.df.adj, gc = as.numeric(sub(pat,"\\1",samp)),
       exp.freq = sub(pat,"\\2",samp)
)-> roc.df.adj

@@

lofreq.df<-mutate(lofreq.df,mutation=paste0(CHROM,"_",REF,POS,ALT))
lofreq.df<-mutate(lofreq.df,category=mutation %in% true_snv$mutant,Id=ID,chr=CHROM,pos=POS,freq.var=AF)
lofreq.df$category[lofreq.df$mutation %in% wt_mut]<-"wt"
lofreq.df$category[lofreq.df$mutation %in% mfe.df$mutation]<-"mfe"
lofreq.df<-ddply(lofreq.df,~chr,primer.cut)

lofreq.df$p.val<-as.numeric(lofreq.df$QUAL) # to make the roc based on the quality scores given by lofreq
lofreq.df<-mutate(lofreq.df, gc = sub(pat,"\\1",Id),
       exp.freq = sub(pat,"\\2",Id)
)
mutate(lofreq.df,exp.freq=ifelse(test = grepl("0",exp.freq),yes=as.numeric(exp.freq)/1000,no = as.numeric(exp.freq)/100))->lofreq.df
lofreq.roc<-hiseq.roc(lofreq.df,possible_tp,possible_vars,"<")

@@

#knitr::kable(subset(lofreq.table,gc==5,select=c(exp.freq,TP,FP)))
lofreq.table<-subset(lofreq.table,gc==5,select=-c(gc,Id)) # don't need the 0.1% sample
rename(lofreq.table,c("exp.freq"="Frequency","TP"="True\nPositives","FP"="False\nPositives"))->lofreq.table
lofreq.table$Frequency<-c("5.0%","2.0%","1.0%","0.5%","0.2%")
lofreq.table$Sensitivity<-round(lofreq.table$Sensitivity,digits=dd)
lofreq.table$Specificity<-round(lofreq.table$Specificity,digits=dd)
lofreq.table<-subset(lofreq.table,select=c("Frequency","Sensitivity","True\nPositives","Specificity","False\nPositives"))
tt2<-ttheme_minimal(colhead=list(fg_params=list(fontface=1,cex=0.65,fontfamily="serif")),core=list(fg_params=list(cex=0.65,fontfamily="serif")))

@@

dup.df<-mutate(dup.df,category=mutation %in% true_snv$mutant) # add Column for True and false variants
dup.df$category[dup.df$mutation %in% wt_mut]<-"wt"
dup.df$category[dup.df$mutation %in% mfe.df$mutation]<-"mfe"

@@

```{r,cache=F}
tabulate(5,c(0.05,0.01,0.005))
#

@@

x<-join(x,y)
x<-subset(x,!(Id%in% c(1240,1241)))
x<-x[order(x$`log10(gc_ul)`,decreasing = T),]
write.csv(x,"../results/tables/table_2.cali_vic.csv")
# ggplot(data,aes(pos,freq.var))+geom_point()+facet_wrap(~chr)
# 
# ggplot(data.cut,aes(pos,freq.var))+geom_point()+facet_wrap(~chr)
# 
# ggplot(data,aes(freq.var))+geom_histogram()+scale_x_log10()
# 
# ggplot(data.cut,aes(freq.var))+geom_histogram()+scale_x_log10()+scale_y_log10()

@@

```{r}
sessionInfo()
```
